Preventing Runtime Errors of Redis at Compile Time

### 2015-11-20 paper.tex
Comments up to section 2.

@@

We began with making Hedis a dynamically checked embedded DSL, and implemented a
 runtime type checker that keeps track of everything. But then we found that
 things can be a lot easier, by leveraging the host language's type checker,
 which also make it statically type-checked!

@@

@@

>>>>

\todo{scm}{say a bit more.}

@@

\todo{scm}{Is this a good thing? Being ``special'' sounds positive.}

We began with making Hedis a dynamically checked embedded DSL, and implemented a runtime type checker that keeps track of types of
each variable. But then we found that things can be a lot easier,
by leveraging the host language's type checker,
which also make it statically type-checked!

\todo{scm}{Elaborate on how the latter approach is easier.}
\todo{scm}{Briefly summarise the approach you use. E.g, ``monadish'',
type of variables are recorded in a list, type level list, etc, such
that readers familiar with the topic will have a rough idea even
without reading on.}

@@

\todo{scm}{I think we have to somehow mention that
not all Hedis programs can be typechecked (even if they might
turn out to be type safe), as a cost of static type checking.}

@@

\todo{scm}{At this point the readers should have some idea
what we are going to do, thus the readers is motivated to
use type-level lists.}
